### 2021-04-13 Paper.tex
modified

Viscous creep and plastic yielding are then combined to obtain a viscoplastic viscosity $\eta_{vp}$, which is computed with an harmonic average \citep{Tackley2010,Glerum2018} as follows
\begin{equation}\label{eq:viscoplastic}
\eta_{vp}=\left(\frac{1}{\eta_{df}}+\frac{1}{\eta_{ds}}+\frac{1}{\eta_{pl}}\right)^{-1}
\end{equation}
Finally, effective viscosity $\eta_{eff}$ is capped by the minimum and the maximum viscosity ($\eta_{min}$ and $\eta_{max}$, respectively) to avoid extremely low or high viscosity \citep{Glerum2018} as follows
\begin{equation}\label{eq:effective}
\eta_{eff}=\min(\max(\eta_{vp},\eta_{min}),\eta_{max})
\end{equation}
Viscous creep and plastic yielding are non-linear rheologies because of their dependence on the velocity field through pressure and strain rates. Therefore, the solution is determined by means of Picard-type iterations, until convergence of the velocity field \citep{Thieulot2011}. The correlation between two consecutive non-linear iterations is given by
\begin{equation}\label{eq:convergence}
\chi=1-\frac{\langle (\bm{v}^i-\langle\bm{v}^i\rangle)\cdot (\bm{v}^{i+1}-\langle\bm{v}^{i+1}\rangle) \rangle}{\sqrt{\sigma^i\sigma^{i+1}}}
\end{equation}
Iterations are performed until either convergence ($\chi<tol$) or maximal number of non-linear iterations ($it_{max}$) is reached.

>>>>

Viscous creep and plastic yielding are then combined to obtain a viscoplastic viscosity $\eta_{vp}$, which is computed with an harmonic average \citep{Tackley2010,Glerum2018} as follows
\begin{equation}\label{eq:viscoplastic}
\eta_{vp}=\left(\frac{1}{\eta_{df}}+\frac{1}{\eta_{ds}}+\frac{1}{\eta_{pl}}\right)^{-1}
\end{equation}
Finally, effective viscosity $\eta_{eff}$ is capped by the minimum and the maximum viscosity ($\eta_{min}$ and $\eta_{max}$, respectively) to avoid extremely low or high viscosity \citep{Glerum2018} as follows
\begin{equation}\label{eq:effective}
\eta_{eff}=\min(\max(\eta_{vp},\eta_{min}),\eta_{max})
\end{equation}
Viscous creep and plastic yielding are non-linear rheologies because of their dependence on the velocity field through pressure and strain rates. Therefore, the solution is determined by means of Picard-type iterations, until convergence of the velocity field \citep{Glerum2018}. The convergence is verified at each iteration $i$ via the nonlinear residual $\bm{\mathcal{R}}^i$ that can be determined as
\begin{equation}\label{eq:convergence}
\bm{\mathcal{R}}^i= \mathbb{K} (\eta_{eff}(\dot{\bm{\epsilon}}^{i-1},p^{i-1}))\cdot \bm{v}^{i-1} - \bm{f}^i
\end{equation}
%\begin{equation}\label{eq:convergence}
%\chi=1-\frac{\langle (\bm{v}^i-\langle\bm{v}^i\rangle)\cdot (\bm{v}^{i+1}-\langle\bm{v}^{i+1}\rangle) \rangle}{\sqrt{\sigma^i\sigma^{i+1}}}
%\end{equation}
%Iterations are performed until either convergence ($\chi<tol$) or maximal number of non-linear iterations ($it_{max}$) is reached.
where $\mathbb{K}$ is the Stiffness matrix and $\bm{f}$ is the right hand side vector \citep{Spiegelman2016,Glerum2018}.  The $L_2$-norm is extracted from $\bm{\mathcal{R}}^i$ and it is normalised using the $L_2$-norm extracted from $\bm{f}^0$. Iterations are performed until either convergence ($\frac{||\bm{\mathcal{R}}^i||_2}{||\bm{f}^0||_2}<tol$) or maximal number of non-linear iterations ($it_{max}$) is reached.
